### 2020-04-15 cv/cv-body.tex
Quick update of CV and PDF links

@@

(\href{https://sean.updog.co/papers/Kuriyama_etal_2016_empirical.pdf}{PDF}).

@@

(\href{https://sean.updog.co/papers/Monnahan_etal_2016_binwidth.pdf}{PDF}).

@@

(\href{https://sean.updog.co/papers/Boudreau_etal_2015_lobster.pdf}{PDF}).

@@

(\href{https://sean.updog.co/papers/Anderson_etal_2015_salmonportfolios.pdf}{PDF}).

@@

(\href{https://sean.updog.co/papers/Anderson_etal_2013_ecological_prophets_with_SOM.pdf}{PDF},

@@

(\href{https://sean.updog.co/papers/Phillis_etal_2012_Multiple_pathways_to_conservation_success.pdf}{PDF},

@@

(\href{https://sean.updog.co/papers/Harnik_etal_2012_Extinctions_in_ancient_and_modern_seas.pdf}{PDF}).

@@

69(8): 1491--1500. \url{https://doi.org/10.1093/icesjms/fss105}
(\href{https://sean.updog.co/Anderson_etal_2012_Assessing_global_marine_fishery.pdf}{PDF}).

@@

(\href{https://sean.updog.co/papers/Anderson_etal_2011_BioScience_with_supplement.pdf}{PDF}).

@@

(\href{https://sean.updog.co/papers/Anderson_etal_2011_seacucumbers_with_supplement.pdf}{PDF}).

@@

(\href{https://sean.updog.co/papers/Anderson_etal_2008_knowledge.pdf}{PDF}).

>>>>

\textbf{Anderson, S.C.}, E.A. Keppel, A.M. Edwards. Reproducible
visualization of raw fisheries data for 113 species improves
transparency, assessment efficiency, and monitoringy. In press at
Fisheries.

@@

(\href{https://www.dropbox.com/s/425a18a4xm9kq8l/Kuriyama_etal_2016_empirical.pdf?dl=1}{PDF}).

@@

(\href{https://www.dropbox.com/s/uksmdtptby9w0ku/Monnahan_etal_2016_binwidth.pdf?dl=1}{PDF}).

@@

(\href{https://www.dropbox.com/s/w027swfx2o8hgvl/Boudreau_etal_2015_lobster.pdf?dl=1}{PDF}).

@@

(\href{https://www.dropbox.com/s/141rsnv5rc7mi5i/Anderson_etal_2015_salmonportfolios.pdf?dl=1}{PDF}).

@@

(\href{https://www.dropbox.com/s/7tx1h1pkmmp222j/Anderson_etal_2013_ecological_prophets_with_SOM.pdf?dl=1}{PDF},

@@

(\href{https://www.dropbox.com/s/cxt848ng5x4hc4t/Phillis_etal_2012_Multiple_pathways_to_conservation_success.pdf?dl=1}{PDF},

@@

(\href{https://www.dropbox.com/s/rdn9685viqr37qy/Harnik_etal_2012_Extinctions_in_ancient_and_modern_seas.pdf?dl=1}{PDF}).

@@

69(8): 1491--1500. \url{https://doi.org/10.1093/icesjms/fss105}.

@@

(\href{https://www.dropbox.com/s/bt16dvi3idw3gdx/Anderson_etal_2011_BioScience_with_supplement.pdf?dl=1}{PDF}).

@@

(\href{https://www.dropbox.com/s/d8id4zxe9xv6jau/Anderson_etal_2011_seacucumbers_with_supplement.pdf?dl=1}{PDF}).

@@

(\href{https://www.dropbox.com/s/b0la81jbqitib6u/Anderson_etal_2008_knowledge.pdf?dl=1}{PDF}).
